---
title: "Consistency of Two-Way Fixed Effects (2FE) Estimator"
output:
    html_document:
        highlight: pygments
---

```{r, include=FALSE}
library(tidyverse)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE, dev = "svg", fig.align = "center")
```

This document use Monte Carlo simulation to show the consistency of Two-Way Fixed Effects Estimator in balanced panel data.

## DGP

```{r}
n_unit <- 5
n_time <- 20

eff_unit <- rep(rnorm(n_unit, -50, 10), n_time) # Draw unit fixed effect
eff_time <- rep(rnorm(n_time, -10, 100), each = n_unit) # Draw time fixed effect

X <- rnorm(n_unit * n_time, 0, 0.5) # Treatment
coef <- 10 # Treatment effect
cons <- 0 # Constant
error <- rnorm(n_unit * n_time, 0, 10)

Y <- cons + coef * X + eff_unit + eff_time + error
```

After our DGP, we can form a data frame like this:
```{r}
df <- data.frame(
    Y = Y,
    X = X,
    unit = as.factor(rep(1:n_unit, n_time)),
    time = as.factor(rep(1:n_time, each = n_unit))
)

df %>%
    head(20) %>%
    knitr::kable()
```

## Scatter plot

Observing unconditional relationship between Y and X, there's hardly any correlation we can see directly:

(The red line is the "real" relationship between X and Y, while blue line indicating fitted line)
```{r, fig.width=4, fig.height=3, out.width="75%"}
ggplot(df, aes(x = X, y = Y, shape = unit)) +
    geom_point() +
    geom_smooth(aes(shape = NULL, color = NULL), formula = y ~ x, method = "lm", se = FALSE) +
    geom_abline(intercept = cons, slope = coef, color = "red")
```

## De-mean Procedure

```{r}
df_fe <- df %>%
    group_by(time) %>%
    mutate(Y_time = mean(Y), X_time = mean(X)) %>%
    ungroup() %>%
    group_by(unit) %>%
    mutate(Y_unit = mean(Y), X_unit = mean(X)) %>%
    ungroup() %>%
    mutate(Y_hat = Y - Y_time - Y_unit + mean(Y), X_hat = X - X_time - X_unit + mean(X))


plot(df_fe$X_hat, df_fe$Y_hat)
points(X, cons + coef * X + error, col = 2)
```

Then estimate its slope:

```{r}
lm(Y_hat ~ -1 + X_hat, data = df_fe) %>% summary()
```

## Regression

If we naively use OLS to estimate the treatment effect, we will get a biased estimator:
```{r}
lm(Y ~ X, data = df) %>% summary()
```

### One-way Fixed Effect

And adding either unit or time fixed effects is not sufficient:

```{r}
lm(Y ~ X + unit, data = df) %>% summary()
lm(Y ~ X + time, data = df) %>% summary()
```

### Two-way Fixed Effects

Instead, we must include unit + time fixed effects to get an unbiased estimation of treatment effect which should be with slope = `r coef`

```{r}
lm(Y ~ X + unit + time, data = df) %>% summary()
```